### 2014-01-06 thesis/src/chapters/chapter-7-evaluation.tex
Thesis: diagrams for a multprovider testcase

\subsection*{Preconditions}

\begin{asparaenum}
  \item[\textbf{Auto-scaling policy specifications}] Policies used in this test are based on a threshold model with the following properties:
  \begin{itemize}
   \item value below 20 should trigger scaling down event
   \item value grater than 60 should trigger scaling up event
  \end{itemize}
  However, considering the fact that we are entirely focused on scaling up, only the upper limit is relevant in our case. Listings \ref{lst:auto-scaling-2cp-carina-service-spec} and \ref{lst:auto-scaling-2cp-cloud-sap-service-spec} presents scaling policies for Carina and Cloud-SAP respectively.

@@

  \lstinputlisting[caption=OpenNebula configuration excerpt -- virtual machine and information manager, label=lst:auto-scaling-2cp-one-config]{auto-scaling-2cp-one-config}
  \lstinputlisting[caption=OpenNebula configuration excerpt -- virtual machine and information manager, label=lst:auto-scaling-2cp-sched-config]{auto-scaling-2cp-sched-config}

  \item[\textbf{Deployment diagrams}]

\subsubsection*{Environment specification}

>>>>

\subsection*{Preconditions}
\subsubsection*{Environment specification}
\begin{asparaenum}
  \item[\textbf{Auto-scaling policy specifications}] Policies used in this test are based on a threshold model with the following properties:
  \begin{itemize}
   \item value below 20 should trigger scaling down event
   \item value grater than 60 should trigger scaling up event
  \end{itemize}
  However, considering the fact that we are entirely focused on scaling up, only the upper limit is relevant in our case. Listings \ref{lst:auto-scaling-2cp-carina-service-spec} and \ref{lst:auto-scaling-2cp-cloud-sap-service-spec} presents scaling policies for Carina and Cloud-SAP respectively.

@@

  \lstinputlisting[caption=OpenNebula configuration excerpt -- virtual machine and information manager, label=lst:auto-scaling-2cp-one-config]{auto-scaling-2cp-one-config}
  \lstinputlisting[caption=OpenNebula configuration excerpt -- scheduler, label=lst:auto-scaling-2cp-sched-config]{auto-scaling-2cp-sched-config}

  \item[\textbf{Deployment diagrams}] Components that took part during testing are show in figures \ref{eval:auto-scaling-2cp-carina-deployment-diagram} and \ref{eval:autoscale-2cp-cloud-sap-deployment-diagram}.

  \begin{figure}[!ht]
    \begin{center}
      \includegraphics{chapter-7/autoscale-2cp-cloud-sap-deployment-diagram}
    \end{center}
    \caption{Auto-scaling - multiple-provider based: deployment diagram of Carina}
    \label{eval:autoscale-2cp-cloud-sap-deployment-diagram}
  \end{figure}

  \begin{figure}[!ht]
    \begin{center}
      \includegraphics{chapter-7/cpu-usage-carina-deployment-diagram}
    \end{center}
    \caption{Auto-scaling - multiple-provider based: deployment diagram of Carina}
    \label{eval:auto-scaling-2cp-carina-deployment-diagram}
  \end{figure}
\end{asparaenum}
